Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-06 paper/paper.tex
hscc17

In this section, we show how to embed discretisation errors on the plant model, as follows: 
%$\hat{G}(z)$ is split into two terms:
%
\begin{equation}
\label{eq:uncertainplant}
%\hat{G}(z)=G(z)+\Delta{G(z)},
\tilde G(z) = \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z),   
\end{equation}
where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$,

\noindent where $G(z)$ is the discretized nominal plant model and
$\Delta{G(z)}$ is the additive uncertainty, which is related to parametric
uncertainties~\cite{Bessa16}.

\subsection{A Uncertainty Model for Quantization Error} 
\label{sec:uncertainty-model-quantization-error}

Here, an uncertainty model to accommodate the
quantization noise effects on $\hat{G}(z)$ is proposed.  As a result,
Eq.~\eqref{eq:uncertainplant} is rewritten as
%
\begin{equation}
\label{eq:uncertainFWLplant}
\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}+\Delta{G_{P}(z)},
\end{equation}

\noindent where $\Delta{G_{Q}(z)}$ represents the quantization uncertainty
model and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model. 
Thus, a model for $\Delta{G_{Q}(z)}$ that can represent the quantization
noise effect in the plant output, and consequently the closed-loop system
output, is proposed.  For convenience, the parametric uncertainties will be
described here.

@@

>>>>

In this section, we show how to embed discretisation errors on the plant model, as follows: 
%$\hat{G}(z)$ is split into two terms:
%
\begin{equation}
\label{eq:uncertainplant}
%\hat{G}(z)=G(z)+\Delta{G(z)},
\tilde G(z) = \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z),   
\end{equation}
where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$, 
$\Delta{G_{Q}(z)}$ represents the quantisation uncertainty model, 
and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.

%\noindent where $G(z)$ is the discretized nominal plant model and
%$\Delta{G(z)}$ is the additive uncertainty, which is related to parametric
%uncertainties~\cite{Bessa16}.

\subsection{An Uncertainty Model for the Quantization Error} 
\label{sec:uncertainty-model-quantization-error}

%Here, an uncertainty model to accommodate the
%quantization noise effects on $\hat{G}(z)$ is proposed.  
%As a result, Eq.~\eqref{eq:uncertainplant} is rewritten as
%
%\begin{equation}
%\label{eq:uncertainFWLplant}
%\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}+\Delta{G_{P}(z)},
%\end{equation}

A model for $\Delta{G_{Q}(z)}$ that can represent the quantization
noise effect in the plant output, and consequently the closed-loop system
output, is proposed.  
\red{[eliminate next:] 
For convenience, the parametric uncertainties will be described here.}

@@

\subsection{Modelling Error on Parameters Representation} 
%\label{sec:}

\red{[TO BE COMPLETED.]}
